Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-25 paper.tex
Martin is only corresponding author
Approve definition of VAWT

% Authors (Add full first names)
\Author{Peter Bachant * and Martin Wosnik *}

@@

% Contact information of the corresponding author (Add [2] after \corres if
% there are more than one corresponding author.)
\corres[2]{\hspace{-1em} Correspondence: pxL3@unh.edu (P.B.);
    martin.wosnik@unh.edu (M.W.); \linebreak Tel.: +1-603-862-1891 \hl {(M.W.)}}
    %please also provide the author (P.B.)'s office number. and please also pay attention to the keywords section, can we define VAWT as vertical-axis wind turbine?

@@

Blackwell \emph{et al.} \cite{Blackwell1976} investigated the effects of
Reynolds number on the performance of a 2 m diameter Darrieus vertical-axis
cross-flow wind turbine with NACA 0012 blades. By varying wind tunnel speed, the
turbine was made to operate at an approximately constant blade chord Reynolds
number $Re_c$ ranging from $1 \times 10^5$ to $3 \times 10^5$. In this regime,
the turbine power coefficient $C_P$ was shown to be sensitive to $Re_c$, with
sensitivity diminishing at the higher Reynolds numbers, especially for turbines
of lower solidity ($Nc/R$, where $N$ is the number of blades and $R$ is the
turbine's maximum radius). More recently, Polagye and Cavagnaro
\cite{Polagye2013b} observed significant Reynolds number sensitivity for a high
solidity helical cross-flow turbine, and Bravo \emph{et al.} \cite{Bravo2007}
observed the power coefficient of a straight-bladed \hl {vertical-axis wind turbine (VAWT)} to become Reynolds
number independent at $Re_c \approx 4 \times 10^5$. Bachant and Wosnik
\cite{Bachant2014} observed Reynolds number independence of the power
coefficient at the optimal tip speed ratio for a high solidity cross-flow
turbine at $Re_D \approx 10^6$ or $Re_{c,\mathrm{avg}} \approx 2 \times 10^5$.

>>>>

% Authors (Add full first names)
\Author{Peter Bachant and Martin Wosnik *}

@@

% Contact information of the corresponding author (Add [2] after \corres if
% there are more than one corresponding author.)
\corres[1]{\hspace{-1em} Correspondence: martin.wosnik@unh.edu;
    \linebreak Tel.: +1-603-862-1891}

@@

Blackwell \emph{et al.} \cite{Blackwell1976} investigated the effects of
Reynolds number on the performance of a 2 m diameter Darrieus vertical-axis
cross-flow wind turbine with NACA 0012 blades. By varying wind tunnel speed, the
turbine was made to operate at an approximately constant blade chord Reynolds
number $Re_c$ ranging from $1 \times 10^5$ to $3 \times 10^5$. In this regime,
the turbine power coefficient $C_P$ was shown to be sensitive to $Re_c$, with
sensitivity diminishing at the higher Reynolds numbers, especially for turbines
of lower solidity ($Nc/R$, where $N$ is the number of blades and $R$ is the
turbine's maximum radius). More recently, Polagye and Cavagnaro
\cite{Polagye2013b} observed significant Reynolds number sensitivity for a high
solidity helical cross-flow turbine, and Bravo \emph{et al.} \cite{Bravo2007}
observed the power coefficient of a straight-bladed vertical-axis wind turbine
(VAWT) to become Reynolds number independent at $Re_c \approx 4 \times 10^5$.
Bachant and Wosnik \cite{Bachant2014} observed Reynolds number independence of
the power coefficient at the optimal tip speed ratio for a high solidity
cross-flow turbine at $Re_D \approx 10^6$ or $Re_{c,\mathrm{avg}} \approx 2
\times 10^5$.
